Supplementary Information for \emph{Parametric controls on vegetation responses to biogeochemical forcing in the CLM5} by Fisher et al. (submitted to JAMES)

### 2019-08-30 SIfigs.tex

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Caxiuan\~a }
     \label{CAX celev}
  \end{figure}

 \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_Br-cax_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 uears of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Caxiuan\~a}
     \label{CAX ndep}
  \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Harvard Forest}
     \label{HRV celev}
  \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US_Ha1_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Harvard Forest}
     \label{HRV ndep}
  \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth, left]{matlab/figures/NOVc_FERT_1CLM50defpft_celev_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of CO$_{2}$ fertilization (550ppm) at Metolius Forest}
     \label{MET celev}
  \end{figure}

  \begin{figure}[h]
    % \centering\includegraphics[width=0.5\textwidth, right]{lion-lo9
     \includegraphics[width=1.3\textwidth,left]{matlab/figures/NOVc_FERT_1CLM50defpft_ndep_1x1pt_US-Me2_ens_MIC_p1_2012.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1) on the influence of 15 years of Nitrogen fertilization (+5 kgN m$^{2}$ y$^{-1}$) at Metolius Forest}
     \label{MET ndep}
  \end{figure}

    \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_TOTVEGC1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on vegetation carbon, across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{VEGC CO2 and N respones 2001}
  \end{figure}

  \begin{figure}[h]
     \centering
     \includegraphics[width=1.55\textwidth, left]{matlab/figures/NOVc_CNdep_LEAFN1__p2012.png}
     \caption{Influence of parametric variation on the impact of 15 years of CO$_{2}$ and N fertilization on leaf nitrogen content ($N_{area}$), across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{Leaf N CO2 and N respones 2001}
  \end{figure}
\end{document}

>>>>

\title{Supplementary Information for \emph{Parametric controls on vegetation responses to biogeochemical forcing in the CLM5} by Fisher et al. (submitted to JAMES)}

    \begin{figure}[h]
     \centering
     \includegraphics[width=1.0\textwidth, left]{matlab/figures/MAY19jp_MEANCOND_-r200_2013TOTSOMN.png}
     \caption{Influence of parametric variation   (over the range tested: -1 to +1, Table \ref{table_ranges}) on the model pre-fertilization state for Nitrogen fixation and total soil N content across the Caxiuan\~a (CAX), Niwot Ridge (NWR), Harvard Forest (HVF) and Metolious MET) sites.}
     \label{MEANSOM}
\end{figure}

\begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_TOTVEGC_y2013.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1, Table 1) on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5 Kg m$^{-2}$ y$^{-1}$ N fertilization, for net primary production (NPP)}
     \label{CN_NPP}
  \end{figure}

    \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_TOTVEGC_y2013.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1, Table 1) on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5 Kg m$^{-2}$ y$^{-1}$ N fertilization, for total vegetation carbon)}
     \label{CN_TOTVEGC}
  \end{figure}

\begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_NFIX_y2013.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1, Table 1) on the model response (fertilized/control) to 15 years of 500ppm CO$_{2}$ and +5 Kg m$^{-2}$ y$^{-1}$ N fertilization, for nitrogen fixation rates (NFIX, gN m^{-2})}
     \label{CN_NFIX}
  \end{figure}

  \begin{figure}[h]
     \includegraphics[width=1.2\textwidth]{matlab/figures/MAY19jp_at_relCNdep_defpft_LEAFN_y2013.png}
     \caption{Influence of parametric variation (over the range tested: -1 to +1, Table 1) on the model response (fertilized/control) to to 15 years of 500ppm CO$_{2}$ and +5 Kg m$^{-2}$ y$^{-1}$ N fertilization, for leaf nitrogen ($N_{leaf}$)}
     \label{CN_LEAFN}
  \end{figure}

\end{document}
